Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-02 docs/evol.tex
minor change

Our experiment involved four entities (see Table~\ref{tbl:exp}):
a number of {\it workers}, a {\it task queue}
mechanism, a {\it data repository}, and the {\it code repository},
which in our case it was the public Maven repository.

\begin{table}
\centering
\begin{threeparttable}
\caption{Experiment Entities}
\label{tbl:exp}
\begin{tabular}{l r r}
\hline
Entity & Software Package & Version\\
\hline
Worker & Custom Python Script & 2.7\\
Task Queue & RabbitMQ\tnote{1} & 3.0.1 \\
Data Repository & MongoDB\tnote{2} & 2.2 \\
Code Repository & Maven Central Repository\tnote{3} & January 2012 \\
\hline
\end{tabular}
 \begin{tablenotes}
       	\item[1] \url{http://www.rabbitmq.com/}
       	\item[2] \url{http://www.mongodb.org/}
	\item[3] \url{http://mvnrepository.com}
   \end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

Our experiment involved four entities (see Table~\ref{tbl:exp}):
a number of {\it workers}, a {\it task queue}
mechanism,\footnote{\url{http://www.rabbitmq.com/}}
a {\it data repository},\footnote{\url{http://www.mongodb.org/}}
and the {\it code repository}, which in our case it was
the public Maven repository.

\begin{table}
\centering
\begin{threeparttable}
\caption{Experiment Entities}
\label{tbl:exp}
\begin{tabular}{l r r}
\hline
Entity & Software Package & Version\\
\hline
Worker & Custom Python Script & 2.7\\
Task Queue & RabbitMQ & 3.0.1 \\
Data Repository & MongoDB & 2.2 \\
Code Repository & Maven Central Repository\tnote{3} & January 2012 \\
\hline
\end{tabular}
\end{threeparttable}
\end{table}
